Solving the power flow problem on integrated transmission-distribution networks: a review and numerical assessment

### 2020-02-06 IEEEtran/paper.tex
werkend gemaakt voor texnic center. Changed pgfplots{1.5} gecomment
Figures added
tables stack vertically

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
 \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
 %\usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
% \usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

@@

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

@@

% packages needed for plotting results
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{pgfplots}
\pgfplotsset{compat=1.15}
\usepackage{multirow}
\usepackage{booktabs} %for fancy tables
\usepackage{adjustbox}

@@

\subsubsection{The Master-Slave iterative schemes}
Two iterative schemes of the Master-Slave splitting are defined \cite{Sun2011}. The first is the Convergence Alternating Iterative (CAI) scheme and the other is the Multistep Alternating Iterative (MAI) scheme. In the CAI-scheme, we define an explicit convergence condition for the slave and for the master. The slave is solved with NR-TCIM, for which we define a tolerance value $\epsilon_D$\todo{Give $\epsilon$}. Once this system has converged, we inject its boundary output into the master. We solve the master using NR-power, for which we also define a (not necessarily) different tolerance value $\epsilon_T$. Once the master has converged, we inject its boundary output into the slave. The integrated network is converged once we have met the convergence condition of the MSS-algorithm. \\
In the MAI-scheme, we define a maximum number of iterations per separate system, ie: $I_{max,D}$ and $I_{max,T}$. We inject the output of one system into the other as soon this maximum number of iterations has been reached. The convergence of the integrated network is still based on the convergence condition of the MSS-algorithm. 
\paragraph{Speeding up the CAI-scheme}
At every MSS iteration, we solve the separated domains on its own. To solve this separated system, we need to initialize the voltages in order to have an initial guess to start Newton-Raphson. In the current suggested schemes, we initialize all the buses, except the boundary bus $B$, to $V=1.0$ pu.\todo{Clarify the coming phrase} We can reduce the number of required iterations for the separate systems if we initialize the voltages to its last obtained solution in the previous MSS-iteration, ie $V^{\nu+1}_0=V^{\nu}_{I,D}$. This will probably be beneficial for the CAI-scheme, where a separated domain requires a couple of iterations before it is converged.  
\newpage 
\section{Numerical assessment of integration methods}
We are testing the unified and splitting methods on several test-cases. We implemented the methods in the Matpower\footnote{MATPOWER is a package of free, open-source Matlab-language M-files for solving steady-state power system simulation and optimization problems \cite{Zimmerman2011}}  library. We created several integrated test cases from existing transmission and distribution test networks. We used the IEEE 9-bus, 118-bus, and 3120-bus data as transmission network test cases. We used the IEEE 13-bus and 37-bus data as distribution test cases. We modified the 13-bus Distribution network to a 10-bus network by deleting the buses connected to a regulator. The 37-bus network is originally a balanced distribution network. We changed it to an unbalanced network by shifting 20\% of the loads of phase b equally to phase a and c, like the original authors \cite{Taranto2008}. \newline
To connect the load buses of the transmission network to the slack bus of the distribution network, we replaced the load-bus by a transformer with the same line impedance as the first distribution cable. We also changed the D-slack bus, the right hand side of the new transformer, to a load bus having the load of the former connecting load bus \cite{Taranto2008}. \newline
From these separated test cases, we created the following combinations: T9-D13, T9-D37, T118-D13, D118-D37, and T3120-D37. All distribution cases are connected by their reference bus. The 9-bus transmission network is connected via bus 7, the 118-bus network via bus 89, and the 3120-bus network via bus 3. We created two new test-cases to see how the integration methods respond when we connect multiple distribution networks to it:  T9-2D13 and T9-3D13, respectively 2 and 3 D13-networks connected to the T9-network. 
% \subsection{Numerical results}
% \begin{table*}[htbp]
% \renewcommand{\arraystretch}{1.3}
% \centering
% \label{tab:resultsPIC3P}
% \begin{adjustbox}{width=1\textwidth}
% \small
% \begin{tabular}{@{}l c cc c cc c cc c cc c cc  @{}}\toprule
%                                       && \multicolumn{2}{c}{\textit{T9-D10}} && \multicolumn{2}{c}{\textit{T30-D37}}&& \multicolumn{2}{c}{\textit{T2383-D13}}  && \multicolumn{2}{c}{\textit{T9-2D10}}  && \multicolumn{2}{c}{\textit{T9-3D10}} \\ \toprule 
% \multicolumn{1}{l}{}                  && \textit{its}      & \textit{CPU}     && \textit{its}       & \textit{CPU}   && \textit{its}       & \textit{CPU}  && \textit{its}      & \textit{CPU}     && \textit{its}       & \textit{CPU}     \\
% \cmidrule{3-4}  \cmidrule{6-7} \cmidrule{9-10} \cmidrule{12-13} \cmidrule{15-16} 
% \multicolumn{1}{l}{}                  && \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{sec}    && \textit{\#}        & \textit{sec}   && \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{sec}        \\ 
% \toprule
% \multicolumn{1}{l}{\textit{F3P}}                    && 4       & 0.559  && 5    & 0.610 &&  5    &  54.1   && 4  & 0.580  && 4  & 0.584  \\ 
% \multicolumn{1}{l}{{\textit{IC}}}                   && 4       & 0.449  && 4    & 0.500 &&  4    &  32.9  && 4  & 0.488  && 4  & 0.473   \\ 
% \multicolumn{1}{l}{{\textit{MS-homo-CAI}}}          && 4       & 0.241  && 3    & 0.258 &&  DNC  &  DNC   && 4  & 0.263  && 4  & 0.272  \\ 
% \multicolumn{1}{l}{{\textit{MS-hybrid-CAI}}}        && 4       & 0.297  && 3    & 0.327 &&  4    &  115   && 4  & 0.324  && 4  & 0.320  \\ 
% \multicolumn{1}{l}{{\textit{MS-homo-MAI(2)}}}       && DNC     & DNC  && DNC    & DNC     &&  DNC  &  DNC   && DNC  & DNC  && DNC & DNC    \\ 
% \multicolumn{1}{l}{{\textit{MS-hybrid-MAI(2)}}}     && 6       & 0.294  && 4    & 0.324     &&  4    &  58     && 6  & 0.334  && 7  & 0.346  \\

% \toprule 
% \end{tabular}
% \end{adjustbox}
% \caption{OLD: Comparison on number of iterations (its) and CPU-time of the different test-cases}
% \end{table*}

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.3}
\centering
\label{tab:resultsPIC3P}\hspace{2cm}
\begin{adjustbox}{width=1\textwidth} %, angle=90}
\small
\begin{tabular}{@{}l c cc c  cccc c cccc c  @{}}\toprule
                               && \multicolumn{2}{c}{\textit{IC}} &&     \multicolumn{4}{c}{\textit{MS-hybrid-CAI}} && \multicolumn{4}{c}{\textit{MS-hybrid-MAI}} \\ \toprule 
\multicolumn{1}{l}{}        && \textit{its}      & \textit{CPU} && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}     &&$I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}      \\
\cmidrule{3-4}  \cmidrule{6-9}  \cmidrule{11-14}   
\multicolumn{1}{l}{}      && \textit{\#}       & \textit{sec} && \textit{\#}      & \textit{\#}    & \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{\#}     &  \textit{\#}       & \textit{sec}  \\
\midrule
\multicolumn{1}{l}{\textit{T9-D13 (7)}}         && 4 & {0.455 } && 4       & 4  & 4 & 0.308 && 6      & 2  & 2 & 0.323  \\
\multicolumn{1}{l}{\textit{T9-D37 (7)}}         && 4 & 0.464    && 3      & 4  & 4 & 0.325 && 6      & 2  & 2 & 0.352  \\
\multicolumn{1}{l}{{\textit{T118-D13 (89)}}}    && 4 & 0.522    && 3      & 7 & 5 & 0.348 && 4 & 2  & 2 & {0.312*} \\
\multicolumn{1}{l}{{\textit{T118-D37 (89)}}}    && 4 & 0.518    && 3      & 7 & 5 & 0.356 && 4 & 2  & 2 & {0.358}\\
\multicolumn{1}{l}{{\textit{T3120-D37 (3003)}}} && 5 & 143      && 3      & 6  & 4  & 383 && 6*  & 2*  & 2* & {235*}  \\
% \multicolumn{1}{l}{\textit{T9-2D13}}       && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
% \multicolumn{1}{l}{{\textit{T9-3D13}}}    && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
\toprule 
\end{tabular}
\end{adjustbox}
\caption{Comparison on number of iterations for hybrid networks (for the MSS-method ($I_{MSS}$) and the necessary iterations per system ($I_T$ and $I_D$)), and CPU-time of the four different MSS-methods, applied on five test-cases. The numbers marked with an asterisk converged to wrong results. In this case, the MAI method required more than 2 subiterations to converge correctly. The slowest CPU times are printed in bold.}
\end{table}

@@

\input{L-N2I1}
\input{L-N1I1}
\input{L-N2I2}
\input{L-N1I2}
\newpage

The results show that most of the methods are good options to solve integrated networks. They converge in a reasonable amount of time and number of iterations and this number is not increasing when the size of the network increases. Only the MS-homogeneous-MAI method is not working properly. The method does not reach convergence. If we take a closer look at the voltage profiles, Figure ... , we see a difference in how this is distributed according to the separated networks. We start with the unified methods. We see a drop at bus $7$, this is the bus connected to the distribution network via a transformer. In the Master-Slave methods we see a different profile at bus $7$: the voltage here is equal to the voltage at the first bus of the distribution network (bus 10 in the plot). But bus $2$ is significantly lower. The results differ, because the MSS-algorithm does not put a transformer in between the two connecting nodes: it uses the input and output directly. So bus $7$ IS bus $1$ of the distribution network. We then must see the voltage drop somewhere else in the transmission network, which we do: mainly at bus 2. This bus is directly connected to bus 7, so now gets less power. \\
Distribution networks are radial, so power flows into the first node and is then distributed to the rest of the network. So all these buses are only influenced by the previous bus. That is why the voltage profiles of distribution networks remains the same, only the voltage magnitude of the entire network is higher, because they receive more power from the connected transmission network, then they would get from the generator when the network is modeled separately. 
\begin{figure*}[h!]
    \centering
    \includegraphics[width=\textwidth]{Images/Enumathpaper.eps}
    \caption{Voltage magnitudes of the different integration methods and separated method. Up: The MSS-methods. Down: The unified methods. Bus 7 and 11 are the buses that are connected.}
    \label{fig:voltmag}
\end{figure*}
\subsection{Speeding-up the computations}
Real transmission and distribution networks, in the Netherlands, have millions of buses. The time to run simulations then becomes really important. In the test-simulations, it is difficult to draw any conclusions from the CPU-time. Only the T2383-D13 network gives a visible difference in CPU-time. As expected, the F3P-method is somewhat slower than the IC-method, and the MSS-methods are even slower. This is logical, because in the F3P-method, the size of the Jacobian increases of being 2n by 2n, to 6n by 6n, n the number of buses in the network. The MSS-method requires 4 iterations, thus solving each the transmission network and distribution network 4 times, instead of one integrated network 4 times. \\
But real networks have another difference, compared to the T2383 network: real distribution networks are much larger than real transmission networks. So the size of transmission networks is not really influencing the speed of computations. Furthermore, very large networks, must be solved in parallel and the MSS-method is some kind of domain-decomposition approach: multiple distribution networks can run on parallel cores and then inject the result to the main core, where the transmission network is solved. Doing new simulations using these speed-up techniques on realistically sized networks, should give a better idea which method is most favourable to solve the integrated power flow problem. 
\section{Discussion}

%\section{References}
\newpage
\bibliographystyle{ieeetr}
\bibliography{pscc3.bib}

>>>>

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
 \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf,position=top]{subfig}
%\else
 %\usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
% \usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e
\usepackage{epstopdf}

@@

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].
%\usepackage{caption}
%\usepackage{subcaption}
\usepackage{tabularx}

@@

% packages needed for plotting results
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{pgfplots}
%\pgfplotsset{compat=1.15}
\usepackage{multirow}
\usepackage{booktabs} %for fancy tables
\usepackage{adjustbox}

@@

\subsubsection{The Master-Slave iterative schemes}
Two iterative schemes of the Master-Slave splitting are defined \cite{Sun2011}. The first is the Convergence Alternating Iterative (CAI) scheme and the other is the Multistep Alternating Iterative (MAI) scheme. In the CAI-scheme, we define an explicit convergence condition for the slave and for the master. The slave is solved with NR-TCIM, for which we define a tolerance value $\epsilon_D$\todo{Give $\epsilon$}. Once this system has converged, we inject its boundary output into the master. We solve the master using NR-power, for which we also define a (not necessarily) different tolerance value $\epsilon_T$. Once the master has converged, we inject its boundary output into the slave. The integrated network is converged once we have met the convergence condition of the MSS-algorithm. \\
In the MAI-scheme, we define a maximum number of iterations per separate system, ie: $I_{max,D}$ and $I_{max,T}$. We inject the output of one system into the other as soon this maximum number of iterations has been reached. The convergence of the integrated network is still based on the convergence condition of the MSS-algorithm. 
\paragraph{Speeding up the CAI-scheme}
At every MSS iteration, we solve the separated domains on its own. To solve this separated system, we need to initialize the voltages in order to have an initial guess to start Newton-Raphson. In the current suggested schemes, we initialize all the buses, except the boundary bus $B$, to $V=1.0$ pu.\todo{Clarify the coming phrase} We can reduce the number of required iterations for the separate systems if we initialize the voltages to its last obtained solution in the previous MSS-iteration, ie $V^{\nu+1}_0=V^{\nu}_{I,D}$. This will probably be beneficial for the CAI-scheme, where a separated domain requires a couple of iterations before it is converged.

\newpage 
\section{Numerical assessment}
All previous mentioned methods are implemented into the Matpower\footnote{MATPOWER is a package of free, open-source Matlab-language M-files for solving steady-state power system simulation and optimization problems \cite{Zimmerman2011}} library. Matpower consists of several transmission network test cases. The resources page of IEEE Power \& Energy Society  contains several distribution network test cases which are all explained in \cite{Schneider2018}. These test cases contain the necessary input to solve power flow problems. We created integrated test test cases from the existing transmission and distribution test cases. We used the IEEE 9-bus, 118-bus, and 3120-bus data as transmission network test cases and the IEEE 13-bus and 37-bus data as distribution test cases. The distribution test cases represent the unbalanced characteristics of the network. We modified the 13-bus distribution network to a 10-bus network by deleting the buses connected to the regulator. We changed the loading of the 37-bus network by shifting 20\% of the loads of phase b equally to phase a and c, just like the original authors \cite{Taranto2008}.
We connected two networks to each other creating the following integrated test cases: 
\begin{itemize}
    \item Test case 1: T9-D13
    \item Test case 2: T9-D37
    \item Test case 3: T118-D37
    \item Test case 4: T3120-D37
    \item Test case 5: T9-2D13 (2 13-bus distribution networks) 
    \item Test case 6: T9-3D13 (3 13-bus distribution networks) 
\end{itemize}
\paragraph{Connection bus}
We selected a random load bus in the transmission network to become the connection bus in the integrated network. We choose bus $7$ in the 9-bus network, we choose bus $118$ in the 118-bus network, and we choose bus $3003$ in the 3120-bus network. This could have been any load bus of the original network. The original reference bus of the distribution network becomes the connection bus in the integrated network. \\
The unified methods puts a transformer between the connection buses. This transformer has the same line admittance as the first distribution cable. The lhs of the transformer is the transmission connection bus, now having zero load. The rhs is the distribution connection bus. This is the former reference bus and must be changed to a load bus having the load as the original transmission connection bus \cite{Taranto2008}. The splitting methods do not put a transformer between the networks. They only change the original transmission load bus to a bus having zero load.   \newline \newline
Test case 5 and 6 have multiple distribution networks connected. These networks are connected to the last 2 and 3 load buses of the transmission networks, where each of the original load bus is changed to a zero load bus. 
\subsection{Results}

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.3}
\centering
\label{tab:resultsPIC3P}\hspace{2cm}
\caption{Comparison on number of iterations for homogeneous networks (for the MSS-method ($I_{MSS}$) and the necessary iterations per system ($I_T$ and $I_D$)), and CPU-time of the four different MSS-methods, applied on five test-cases. The numbers marked with an asterisk converged to wrong results. In this case, the MAI method required more than 2 subiterations to converge correctly. The slowest CPU times are printed in bold. The top one are methods applied on hybrid networks. The bottom one is applied on homogeneous networks. }
\subfloat[Hybrid networks]{
\begin{adjustbox}{width=1\textwidth} %, angle=90}
\small
\begin{tabular}{@{}l c cc c  cccc c cccc c  @{}}\toprule
                               && \multicolumn{2}{c}{\textit{IC}} &&     \multicolumn{4}{c}{\textit{MS-hybrid-CAI}} && \multicolumn{4}{c}{\textit{MS-hybrid-MAI}} \\ \toprule 
\multicolumn{1}{l}{}        && \textit{its}      & \textit{CPU} && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}     &&$I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}      \\
\cmidrule{3-4}  \cmidrule{6-9}  \cmidrule{11-14}   
\multicolumn{1}{l}{}      && \textit{\#}       & \textit{sec} && \textit{\#}      & \textit{\#}    & \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{\#}     &  \textit{\#}       & \textit{sec}  \\
\midrule
\multicolumn{1}{l}{\textit{T9-D13 (7)}}         && 4 & {0.455 } && 4       & 4  & 4 & 0.308 && 6      & 2  & 2 & 0.323  \\
\multicolumn{1}{l}{\textit{T9-D37 (7)}}         && 4 & 0.464    && 3      & 4  & 4 & 0.325 && 6      & 2  & 2 & 0.352  \\
\multicolumn{1}{l}{{\textit{T118-D13 (89)}}}    && 4 & 0.522    && 3      & 7 & 5 & 0.348 && 4 & 2  & 2 & {0.312*} \\
\multicolumn{1}{l}{{\textit{T118-D37 (89)}}}    && 4 & 0.518    && 3      & 7 & 5 & 0.356 && 4 & 2  & 2 & {0.358}\\
\multicolumn{1}{l}{{\textit{T3120-D37 (3003)}}} && 5 & 143      && 3      & 6  & 4  & 383 && 6*  & 2*  & 2* & {235*}  \\
% \multicolumn{1}{l}{\textit{T9-2D13}}       && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
% \multicolumn{1}{l}{{\textit{T9-3D13}}}    && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
\toprule 
\end{tabular}
\end{adjustbox}}

\hspace{-2.5cm}
\subfloat[Homogeneous networks]{
%\caption{.}
\label{tab:resultsPIC3P}\hspace{2cm}
\begin{adjustbox}{width=1\textwidth} %, angle=90}
\small
\begin{tabular}{@{}l c cc c  cccc c cccc c  @{}}\toprule
                               && \multicolumn{2}{c}{\textit{F3P}} &&     \multicolumn{4}{c}{\textit{MS-homo-CAI}} && \multicolumn{4}{c}{\textit{MS-homo-MAI}} \\ \toprule 
\multicolumn{1}{l}{}        && \textit{its}      & \textit{CPU} && $I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}     &&$I_{MSS}$      & $I_T$   &  $I_D$      & \textit{CPU}      \\
\cmidrule{3-4}  \cmidrule{6-9}  \cmidrule{11-14}   
\multicolumn{1}{l}{}      && \textit{\#}       & \textit{sec} && \textit{\#}      & \textit{\#}    & \textit{\#}       & \textit{sec}     && \textit{\#}        & \textit{\#}     &  \textit{\#}       & \textit{sec}  \\
\midrule
\multicolumn{1}{l}{\textit{T9-D13 (7)}}      && 4 &\textbf{ 0.610}  && 4 & 4 & 4 &  0.237 && 6       & 2 & 2  & {0.257}\\
\multicolumn{1}{l}{\textit{T9-D37 (7)}}      && 4 & \textbf{0.587}    && 3 & 4 & 4 &  0.262 && 6       & 2 & 2  & {0.299}\\
\multicolumn{1}{l}{{\textit{T118-D13 (89)}}}   && 5 & \textbf{0.763}     && 3       & 7 & 5  & 0.324 && 4  & 2 &2 &  0.297  \\
\multicolumn{1}{l}{{\textit{T118-D37 (89)}}}   && 5 & \textbf{0.920}    && 3       & 7 & 5  & 0.360 && 4 & 2 & 2 &  0.325 \\
\multicolumn{1}{l}{{\textit{T3120-D37 (3003)}}}   && 5 & \textbf{2438}   &&  3 & 6  & 4  & 1213  && 6 & 2 & 2 &  841    \\
% \multicolumn{1}{l}{\textit{T9-2D13}}       && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
% \multicolumn{1}{l}{{\textit{T9-3D13}}}    && - & - && - & -    && -       & - & -  & \textbf{-} && -   & - & - &  - && -       & -  & - & - && -       & -  & - & - \\
\toprule 
\end{tabular}
\end{adjustbox}}

@@

\input{L-N2I1}
\input{L-N1I1}
\input{L-N2I2}
\input{L-N1I2}
\newpage 
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Images/MAI_N1.eps}
\caption{Hybrid networks}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{Images/Z_MAI_N1.eps}
\caption{Hybrid networks}
\end{figure}
\newpage
The results show that most of the methods are good options to solve integrated networks. They converge in a reasonable amount of time and number of iterations and this number is not increasing when the size of the network increases. Only the MS-homogeneous-MAI method is not working properly. The method does not reach convergence. If we take a closer look at the voltage profiles, Figure ... , we see a difference in how this is distributed according to the separated networks. We start with the unified methods. We see a drop at bus $7$, this is the bus connected to the distribution network via a transformer. In the Master-Slave methods we see a different profile at bus $7$: the voltage here is equal to the voltage at the first bus of the distribution network (bus 10 in the plot). But bus $2$ is significantly lower. The results differ, because the MSS-algorithm does not put a transformer in between the two connecting nodes: it uses the input and output directly. So bus $7$ IS bus $1$ of the distribution network. We then must see the voltage drop somewhere else in the transmission network, which we do: mainly at bus 2. This bus is directly connected to bus 7, so now gets less power. \\
Distribution networks are radial, so power flows into the first node and is then distributed to the rest of the network. So all these buses are only influenced by the previous bus. That is why the voltage profiles of distribution networks remains the same, only the voltage magnitude of the entire network is higher, because they receive more power from the connected transmission network, then they would get from the generator when the network is modeled separately. 
\begin{figure*}[h!]
    \centering
    \includegraphics[width=\textwidth]{Images/Enumathpaper.eps}
    \caption{Voltage magnitudes of the different integration methods and separated method. Up: The MSS-methods. Down: The unified methods. Bus 7 and 11 are the buses that are connected.}
    \label{fig:voltmag}
\end{figure*}
\subsection{Speeding-up the computations}
Real transmission and distribution networks, in the Netherlands, have millions of buses. The time to run simulations then becomes really important. In the test-simulations, it is difficult to draw any conclusions from the CPU-time. Only the T2383-D13 network gives a visible difference in CPU-time. As expected, the F3P-method is somewhat slower than the IC-method, and the MSS-methods are even slower. This is logical, because in the F3P-method, the size of the Jacobian increases of being 2n by 2n, to 6n by 6n, n the number of buses in the network. The MSS-method requires 4 iterations, thus solving each the transmission network and distribution network 4 times, instead of one integrated network 4 times. \\
But real networks have another difference, compared to the T2383 network: real distribution networks are much larger than real transmission networks. So the size of transmission networks is not really influencing the speed of computations. Furthermore, very large networks, must be solved in parallel and the MSS-method is some kind of domain-decomposition approach: multiple distribution networks can run on parallel cores and then inject the result to the main core, where the transmission network is solved. Doing new simulations using these speed-up techniques on realistically sized networks, should give a better idea which method is most favourable to solve the integrated power flow problem. 
\section{Discussion}

%\section{References}
\newpage
\bibliographystyle{ieeetr}
\bibliography{pscc3}
